---
title: "Plot annotation counts"
output: html_notebook
---

```{r}
library(glue)
library(tidyverse)
```


```{r}
df_counts <-  read_csv("output/qc_annotations_counts.csv")
```


```{r}
df_counts_long <-
  df_counts %>%
  pivot_longer(
    c(Debris, Empty, Blurry, Good),
    names_to = "category",
    values_to = "count"
  )
```



```{r rows.print=50}
df_counts_long_report <- 
  df_counts_long %>%
  filter(category != "Good") %>%
  group_by(setname,
           filename,
           is_nd2,
           Image_Metadata_Plate,
           n_sites,
           n_channels,
           n_images,
           image_width,
           annot_type) %>%
  summarize(count = sum(count), .groups = "keep") %>%
  pivot_wider(names_from = "annot_type",
              values_from = "count",
              names_prefix = "count_") %>%
  mutate(
    frac_user = round(count_user / n_images, 2),
    frac_cpa = round(count_cpa / n_images, 2)
  ) %>%
  arrange(setname, is_nd2, Image_Metadata_Plate, n_sites, n_channels)

df_counts_long_report

df_counts_long_report %>%
  write_csv("output/qc_annotations_counts_report.csv")
```


```{r fig.height=6}
df_counts_long %>% 
  distinct(Image_Metadata_Plate, filename, n_images, is_nd2) %>%
  ggplot(aes(paste(filename, Image_Metadata_Plate, sep = ":"), n_images)) +
  geom_col() +
  xlab("Plate") +
  facet_grid(
    is_nd2 ~ .,
    labeller = labeller(.rows = label_both),
    scales = "free_y",
    space = "free"
  ) + coord_flip()
```


```{r fig.height=6}
df_counts_long %>% 
  distinct(Image_Metadata_Plate, filename, n_sites, is_nd2) %>%
  ggplot(aes(paste(filename, Image_Metadata_Plate, sep = ":"), n_sites)) +
  geom_col() +
  xlab("Plate") +
  facet_grid(
    is_nd2 ~ .,
    labeller = labeller(.rows = label_both),
    scales = "free_y",
    space = "free"
  ) + coord_flip()
```


```{r fig.height=6, fig.width=10}
df_counts_long %>% 
  filter(category != "Good") %>%
  ggplot(aes(paste(filename, Image_Metadata_Plate, sep = ":"), count / n_images, fill = category)) +
  geom_col() +
  xlab("Plate") +
  scale_y_continuous(labels = ~scales::percent(., accuracy = 1)) +
  facet_grid(
    is_nd2 ~ annot_type,
    labeller = labeller(.rows = label_both),
    scales = "free_y",
    space = "free"
  ) + 
  coord_flip()
```
```{r fig.height=10, fig.width=10}
df_counts_long %>% 
  filter(category != "Good") %>%
  ggplot(aes(annot_type, count / n_images, fill = category)) +
  geom_col() +
  scale_y_continuous(labels = ~scales::percent(., accuracy = 1)) +
  facet_wrap(~Image_Metadata_Plate, ncol = 5, scales = "free_y") +
  theme(strip.text = element_text(size = 7))
```

```{r}
df_count_total <-
  df_counts %>% 
  group_by(is_nd2, annot_type) %>%
  summarize(across(one_of("Debris", "Empty", "Blurry", "Good"), sum), .groups = "keep") %>%
  pivot_longer(-c(is_nd2, annot_type),  names_to = "category", values_to = "count") 
```


```{r}
df_counts_long %>%
  filter(category != "Good") %>%
  ggplot(aes(category, count, fill = Image_Metadata_Plate)) +
  geom_col() +
  geom_label(
    data = df_count_total %>%   filter(category != "Good"),
    aes(category, count,
        label = count),
    fill = "white"
  ) +
  theme(legend.position = "none") +
  ggtitle("Number of images per category", subtitle = "Color indicates plate") +
  facet_grid(is_nd2 ~ annot_type, labeller = labeller(.rows = label_both))
```

Also plot "Good" class.

We should only consider the CPA version of "Good" to be conservative because of this:

>  The protocol was for the scorers to hand-check all of the CPA non-Good predictions, but not the CPA Good predictions


```{r}
df_counts_long %>%
  filter(category == "Good") %>%
  ggplot(aes(category, count, fill = Image_Metadata_Plate)) +
  geom_col() +
  geom_label(
    data = df_count_total %>%   filter(category == "Good"),
    aes(category, count,
        label = count),
    fill = "white"
  ) +
  theme(legend.position = "none") +
  ggtitle("Number of images per category", subtitle = "Color indicates plate.") +
  facet_grid(is_nd2 ~ annot_type, labeller = labeller(.rows = label_both))
```


```{r}
arpit_counts <-
  df_counts_long %>%
  filter(filename != "Classifier_Nikon_10X_Batch9-Pearl") %>%
  filter(!(category == "Blurry" & image_width <= 2000)) %>%
  filter(!is_nd2)

arpit_counts_summary <- 
  arpit_counts %>%
  group_by(annot_type, category) %>%
  summarize(count = sum(count), .groups = "keep") %>%
  pivot_wider(names_from = "annot_type", values_from = "count", names_prefix = "count_")

arpit_counts_summary %>%
  write_csv("output/arpit_counts_summary.csv")

arpit_counts %>%
  filter(category != "Good") %>%
  ggplot(aes(category, count, fill = Image_Metadata_Plate)) +
  geom_col() +
  geom_label(
    data =
      arpit_counts %>%
      group_by(annot_type, category) %>%
      summarize(count = sum(count), .groups = "keep") %>%
      filter(category != "Good"),
    aes(category, count,
        label = count),
    fill = "white"
  ) +
  theme(legend.position = "none") +
  ggtitle("Number of images per category", subtitle = "Color indicates plate") +
  facet_grid(is_nd2 ~ annot_type, labeller = labeller(.rows = label_both))
```

Total counts available are shown below

Recap: we should only consider the CPA version of "Good" to be conservative because of this:

>  The protocol was for the scorers to hand-check all of the CPA non-Good predictions, but not the CPA Good predictions

```{r}
df_counts_long %>%
  group_by(annot_type, category) %>%
  summarize(count = sum(count), .groups = "keep") %>%
  pivot_wider(names_from = "annot_type", values_from = "count", names_prefix = "count_")
```


```{r}
df_counts %>%
  pivot_longer(c(Debris, Empty, Blurry, Good),
               names_to = "category",
               values_to = "count") %>%
  pivot_wider(names_from = "annot_type",
              values_from = "count",
              names_prefix = "count_") %>%
  filter(category != "Good") %>%
  ggplot(aes(count_user / n_images, count_cpa / n_images)) +
  geom_point(aes(color = count_user > count_cpa)) +
  facet_wrap( ~ category) +
  geom_abline(slope = 1) +
  coord_equal() +
  scale_x_continuous(labels = ~scales::percent(., accuracy = 1)) +
  scale_y_continuous(labels = ~scales::percent(., accuracy = 1)) +
  ggtitle("Counts of images tagged as belonging to each class",
          subtitle = "Each channel is counted separately") +
  theme(legend.position = "bottom")
```
```{r fig.height=10, fig.width=13}
df_counts %>%
  pivot_longer(c(Debris, Empty, Blurry, Good),
               names_to = "category",
               values_to = "count") %>%
  pivot_wider(names_from = "annot_type",
              values_from = "count",
              names_prefix = "count_") %>%
mutate(cpa_is_zero = count_cpa == 0) %>%
mutate(count_cpa = count_cpa + .Machine$double.eps,
         count_user = count_user + .Machine$double.eps,
         ratio_user_to_cpa = count_user / count_cpa,
         ratio_user_to_cpa = ifelse(ratio_user_to_cpa > 2, Inf, ratio_user_to_cpa))  %>%
  filter(category != "Good") %>%
  ggplot(aes(paste(filename, Image_Metadata_Plate, sep = ":"), ratio_user_to_cpa)) +
  geom_col(aes(fill = cpa_is_zero)) +
  geom_label(aes(y = -.05, label = round(count_user, 0)), hjust = "right") +
  xlab("Plate") +
  ylim(c(-.5, 1.5)) +
  facet_grid(
    is_nd2 ~ category,
    labeller = labeller(.rows = label_both),
    scales = "free_y",
    space = "free"
  ) + 
  geom_hline(yintercept = 0.85, color = "red", alpha = 0.5) +
  geom_hline(yintercept = 1.15, color = "red", alpha = 0.5) +
  coord_flip() + 
  ggtitle("Ratio of User:CPA -labelled images", subtitle = "User-labeled counts are indicated with labels")
```
Debris annotations

```{r}
MyTrainingSet_5channel_urls <-
  read_csv(
    "input/debris_annotations/MyTrainingSet_5channel_urls.csv",
    col_types = cols()
  )
```

```{r}
MyTrainingSet_5channel_urls %>% count()

MyTrainingSet_5channel_urls %>%
  distinct(Image_Metadata_Plate,
           Image_Metadata_Well,
           Image_Metadata_Site) %>%
  count()
```

```{r}
debris_counts <-
  MyTrainingSet_5channel_urls %>%
  distinct(Image_Metadata_Plate,
           Image_Metadata_Well,
           Image_Metadata_Site) %>%
  count(Image_Metadata_Plate, name = "Debris_sites_annotated") %>%
  inner_join(df_counts %>% filter(annot_type == "user"),
             by = c("Image_Metadata_Plate"))


debris_counts %>%
  ggplot(aes(paste(filename, Image_Metadata_Plate, sep = ":"), Debris_sites_annotated)) + 
  geom_col() + 
  xlab("Plate") +
  coord_flip()

debris_counts %>%
  ggplot(aes(paste(filename, Image_Metadata_Plate, sep = ":"), Debris_sites_annotated/sum(Debris_sites_annotated))) + 
  geom_col() + 
  xlab("Plate") +
  ylab("Percentage of total count") +
  scale_y_continuous(labels = ~scales::percent(., accuracy = 1)) +
  coord_flip()
```


```{r rows.print=20}
debris_counts %>%
  mutate(Debris_sites = Debris / n_channels) %>%
  mutate(diff = Debris_sites_annotated - Debris_sites) %>%
  select(Image_Metadata_Plate, Debris_sites_annotated, Debris_sites, diff)
```

