---
title: "Generate CellProfiler feature set"
output: html_notebook
---

```{r}
library(tidyverse)
```

# Broad

```{r}
broad_qc <- 
  arrow::read_parquet("output/qc_annotations.parquet")
```

Apply Arpit's filters

```{r}
broad_qc <-
  broad_qc %>%
  filter(filename != "Classifier_Nikon_10X_Batch9-Pearl") %>%
  filter(!(UserAnnotation_Blurry == 1 & image_width <= 2000)) %>%
  filter(!is_nd2)
```


```{r}
broad_qc_user <-
  broad_qc %>%
  select(
    Image_Metadata_Plate,
    Image_Metadata_Well,
    Image_Metadata_Site,
    matches("UserAnnotation"),
    matches("Image_ImageQuality"),
    matches("Image_URL_")
  ) %>%
  rename_with( ~ str_remove(., "UserAnnotation_"), .cols = matches("UserAnnotation_"))

broad_qc_cpa <-
  broad_qc %>%
  select(
    Image_Metadata_Plate,
    Image_Metadata_Well,
    Image_Metadata_Site,
    matches("CPAScore"),
    matches("Image_ImageQuality"),
    matches("Image_URL_")
  ) %>%
  rename_with( ~ str_remove(., "CPAScore_"), .cols = matches("CPAScore_")) %>%
  rename_with( ~ str_remove(., "ImageCount"), .cols = matches("ImageCount")) 

stopifnot(all(names(broad_qc_cpa) == names(broad_qc_user)))

broad_qc <-
  bind_rows(
    broad_qc_cpa %>% mutate(source = "cpa", .before = "Image_Metadata_Plate"),
    broad_qc_user %>% mutate(source = "user", .before = "Image_Metadata_Plate")
  )

rm(broad_qc_cpa)
rm(broad_qc_user)
```


```{r}
get_channel_data <-
  function(channel, df) {
    df %>%
      select(-matches("Image_ImageQuality|Image_URL_"),
             matches(paste0("Image_URL_.*", channel)),
             matches(paste0("Image_ImageQuality_.*", channel))) %>%
      rename_with( ~ str_remove(., paste0("_", channel)),
                   .cols = matches(channel)) %>%
      rename_with( ~ str_remove(., "^Image_"),
                   .cols = matches("^Image_ImageQuality_")) %>%
      mutate(Image_URL = Image_URL %>%
               str_remove("file:\\\\home\\\\ubuntu\\\\bucket\\\\projects\\\\2019_07_11_JUMP-CP-pilots\\\\") %>%
               str_replace_all("\\\\", "/")
               ) %>%
      mutate(channel = str_remove(channel, "^Orig"), .before = "source") %>%
      select(-any_of(
        c(
          "ImageQuality_ThresholdOtsu_2W",
          "ImageQuality_ThresholdOtsu_3FW"
        )
      )) # remove because not present in all
  }
```


```{r}
broad_qc <- 
  c("OrigDNA", "OrigRNA", "OrigER", "OrigMito", "OrigAGP", "OrigActin", "OrigGolgi") %>%
  map_df(function(channel) get_channel_data(channel, broad_qc)) %>%
  na.omit()
```

NOTE: This mapping does not allow multiple labels for an image!

```{r}
broad_qc <-
  broad_qc %>%
  mutate(Class = case_when(
    Debris == 1 ~ "Debris",
    Empty == 1 ~ "Empty",
    Blurry == 1 ~ "Blurry",
    Good == 1 ~ "Good"
  ))
```


```{r}
broad_qc %>%
  filter(source == "cpa" &
           Image_Metadata_Plate == "Plate3_PCO_6ch_4site_10XPA_Crestz") %>%
  count(Class) %>% 
  arrange(Class)
```
```{r}
broad_qc %>%
  filter(source == "cpa" &
           Image_Metadata_Plate == "Plate3_PCO_6ch_4site_10XPA_Crestz") %>%
  summarise(across(matches("Debris|Empty|Blurry|Good"), sum)) %>%
  pivot_longer(everything(), names_to = "Class", values_to = "n") %>% 
  arrange(Class)
```
The difference in Good counts is because some wells are labeled Good + some other class

```{r}
broad_qc %>%
  filter(source == "cpa" &
           Image_Metadata_Plate == "Plate3_PCO_6ch_4site_10XPA_Crestz") %>%
  filter(Debris + Blurry + Empty + Good > 1) %>%
  count()
```


```{r}
broad_qc <- 
  broad_qc %>% 
  mutate(Metadata_Partner = "Broad") %>%
  select(Class,
         Metadata_Partner,
         Metadata_Source = source,
         Metadata_Plate = Image_Metadata_Plate,
         Metadata_Well = Image_Metadata_Well,
         Metadata_Site = Image_Metadata_Site,
         Metadata_Channel = channel,
         Metadata_FileLocation = Image_URL,
         matches("ImageQuality_"))
```


```{r}
MyTrainingSet_5channel_urls <-
  read_csv("input/debris_annotations/MyTrainingSet_5channel_urls.csv",
           col_types = cols())

MyTrainingSet_5channel_urls %>% count()

debris_images <-
  MyTrainingSet_5channel_urls %>%
  select(
    Metadata_Plate = Image_Metadata_Plate,
    Metadata_Well = Image_Metadata_Well,
    Metadata_Site = Image_Metadata_Site,
    Metadata_Channel = Class
  ) %>% 
  mutate(Class = "Debris", .before = "Metadata_Plate")
```

These 7 sites don't have measurements transferred over because they had multiple labels, which was filtered out when writing `qc_annotations.parquet`

```{r}
debris_images %>%
  anti_join(
    broad_qc %>% filter(Metadata_Source == "user") ,
    by = c(
      "Metadata_Plate",
      "Metadata_Well",
      "Metadata_Site",
      "Metadata_Channel"
    )
  )
```


```{r}
broad_qc <-
  bind_rows(
    broad_qc %>% filter(!(Class == "Debris" & Metadata_Source == "user")),
    broad_qc %>% filter((Class == "Debris" & Metadata_Source == "user")) %>%
      inner_join(
        debris_images,
        by = c(
          "Class",
          "Metadata_Plate",
          "Metadata_Well",
          "Metadata_Site",
          "Metadata_Channel"
        )
      ),
  )
```


```{r}
broad_qc %>%
  filter(Metadata_Source == "cpa" &
           Metadata_Plate == "Plate3_PCO_6ch_4site_10XPA_Crestz") %>%
  count(Class)
```

Debris counts will be 201 instead of 208 because 7 got dropped because of duplicate labels

```{r}
broad_qc %>%
  filter(Metadata_Source == "user") %>%
  group_by(Metadata_Partner, Class) %>%
  tally(name = "n_images") 
```

# Partners 

```{r eval=FALSE}
partner_qc <- 
  read_csv("input/2021_04_16_QCImages_QC_Image.csv.gz", guess_max = Inf)

partner_qc %>% 
  arrow::write_parquet("input/2021_04_16_QCImages_QC_Image.parquet")
```


```{r}
partner_qc <-
  arrow::read_parquet("input/2021_04_16_QCImages_QC_Image.parquet")
```


```{r}
partner_qc <-
  partner_qc %>% 
  select(Metadata_FileLocation, matches("^ImageQuality_")) %>%
  rename_with(~ str_remove(., "_DNA"), .cols = matches("_DNA"))
```


```{r}
broad_features <- 
  names(broad_qc) %>% str_subset("ImageQuality_")

partner_features <- 
  names(partner_qc) %>% str_subset("ImageQuality_")

stopifnot(all(partner_features == partner_features))
```


```{r}
partner_annotations_with_metadata <- 
  read_csv("input/partner_annotations_with_metadata.csv", col_types = cols()) %>%
  mutate(Metadata_FileLocation = 
           str_remove(`Image Path`, "/dgx1nas1/cellpainting-datasets/2019_07_11_JUMP_CP_pilots/"),
         .before = "Partner") %>%
  select(-`Image Path`) %>%
  rowwise() %>%
  mutate(Metadata_FileLocation = URLdecode(Metadata_FileLocation)) %>%
  ungroup()
```


```{r}
partner_qc <-
  partner_qc %>%
  mutate(
    Metadata_FileLocation = Metadata_FileLocation %>%
      str_remove("file:///D:/2019_07_11_JUMP-CP-pilots/") %>%
      str_replace("Ksilink%20-%20U2OS", "Ksilink_U2OS") %>%
      str_replace("Ksilink%20-%20WT004", "Ksilink_WT004")
  ) %>%
  rowwise() %>%
  mutate(Metadata_FileLocation = URLdecode(Metadata_FileLocation)) %>%
  ungroup()
```


```{r}
partner_qc <-
  partner_annotations_with_metadata %>%
  inner_join(partner_qc, by = "Metadata_FileLocation")
```


Merck channel mapping

W1: Cy5: MitoTracker (Mitochondria)
W2: Texas Red: Phalloidin (Actin)
W3: Cy3: WGA/Syto-14 (Golgi/Nucleolus)
W4: FITC: Concanavalin A (ER)
W5: DAPI: Nuclei

```{r}
partner_qc <-
  partner_qc %>%
  mutate(
    Channel = 
      case_when(
        Channel == "w1" ~ "Mito",
        Channel == "w2" ~ "Actin",
        Channel == "w3" ~ "RNA_Golgi",
        Channel == "w4" ~ "ER",
        Channel == "w5" ~ "DNA",
        TRUE ~ Channel
      )
  )
```


```{r}
partner_qc <- 
  partner_qc %>% 
  mutate(Metadata_Source = "user",
         Metadata_Site = -1) %>%
  select(Class,
         Metadata_Source,
         Metadata_Partner = Partner,
         Metadata_Plate = Plate,
         Metadata_Well = Well,
         Metadata_Site,
         Metadata_Channel = Channel,
         Metadata_FileLocation,
         matches("ImageQuality_"))
```


```{r}
partner_qc %>%
  filter(Metadata_Source == "user") %>%
  count(Class, Metadata_Partner)
```


```{r}
partner_qc %>%
  filter(Metadata_Source == "user") %>%
  group_by(Metadata_Partner, Class) %>%
  tally(name = "n_images") %>%
  ggplot(aes(Metadata_Partner, n_images)) +
  geom_col() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2), drop = FALSE) +
  geom_label(aes(label = n_images)) +
  facet_grid( ~ Class, space = "free", scales = "free_x") 
```

# Combine 

```{r}
combined_qc <-
  bind_rows(
    broad_qc,
    partner_qc
  )
```


```{r}
combined_qc %>%
  arrow::write_parquet("output/qc_features_annotations_full.parquet")
```

